Improving Code Completion in Pharo\\Using N-gram Language Models

### 2020-05-15 ACM/abstract.tex
minor fixes

@@

\end{abstract}
\keywords{Pharo, code completion, IDE, statistical models}
\maketitle
\bibliographystyle{ACM-Reference-Format}
\bibliography{rmod,others}
\end{document}

>>>>

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007</concept_id>
<concept_desc>Software and its engineering</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[300]{Software and its engineering}

@@

\end{abstract}
\keywords{Pharo, code completion, IDE, statistical models, dynamically typed languages, Smalltalk}
\maketitle
\bibliographystyle{ACM-Reference-Format}
\bibliography{rmod,others}
\end{document}
